---
title: Replicate research studies for knowledge development
author: Gabriel Cabrera
date: '2019-02-23'
slug: replicate-research-studies-for-knowledge-development
categories:
  - Econometrics
  - Finance
tags:
  - R
lastmod: '2019-02-23T23:54:27-03:00'
layout: post
type: post
highlight: no
draft: true
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, comment = "#")
library(fontawesome)
```

# Forecasting stock returns

1. Forecasting stock returns (Rapach and Zhou, 2013)

    `r fa("download", fill = "#ee5863")` 
    ```{r echo = FALSE} 
    xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
      name = "data.xlsx")
    ```   
    
    - Monthly U.S. equity premium out-of-sample forecasting results based on 
      individual economic variables with unrestricted and Predictive regression 
      forecasts with Campbell and Thompson (2008). 
  
       `r fa("download", fill = "#ee5863")` 
       ```{r echo = FALSE} 
       xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
         name = "R code.xlsx")
       ```  
       &ensp;&ensp;
       `r fa("desktop", fill = "forestgreen")` 
       [View post](https://gcabrerag.rbind.io/)
    
2. International Stock-Return Predictability (Rapach, Strauss and Zhou, 2013)

    `r fa("download", fill = "#ee5863")` 
    ```{r echo = FALSE} 
    xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
      name = "data.xlsx")
    ```   

    - Benchmark predictive regression model estimation from 1980:02 to 2010:12.
      The countries are Australia, Canada, France, Germany, Italy, Japan, 
      Netherlands, Sweden, Switzerland, United Kingdom and United States.
      The significance level come from a wild bootstrapped p-values.
    
       `r fa("download", fill = "#ee5863")` 
       ```{r echo = FALSE} 
       xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
         name = "R code.xlsx")
       ```  
       &ensp;&ensp;
       `r fa("desktop", fill = "forestgreen")` 
       [View post](https://gcabrerag.rbind.io/)
      
3. Forecasting the Equity Risk Premium: The Role of Technical Indicators (Neely, Rapach, Tu and Zhou)

    `r fa("download", fill = "#ee5863")` 
    ```{r echo = FALSE} 
    xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
      name = "data.xlsx")
    ```   

    - Summary Statistics, December 1950 to December 2011. 
  
       `r fa("download", fill = "#ee5863")` 
       ```{r echo = FALSE} 
       xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
         name = "R code.xlsx")
       ```  
       &ensp;&ensp;
       `r fa("desktop", fill = "forestgreen")` 
       [View post](https://gcabrerag.rbind.io/)
      
4. Short interest and aggregate stock returns (Rapach, Ringgenberg and Zhou, 2016)

    `r fa("download", fill = "#ee5863")` 
    ```{r echo = FALSE} 
    xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
      name = "data.xlsx")
    ```   

    - Summary Statistics and predictor variable correlation, 
      from 1973:01 to 2014:12. 
      
       `r fa("download", fill = "#ee5863")` 
       ```{r echo = FALSE} 
       xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
         name = "R code.xlsx")
       ```  
       &ensp;&ensp;
       `r fa("desktop", fill = "forestgreen")` 
       [View post](https://gcabrerag.rbind.io/)

    - In-sample predictive regression estimation results, from  1973:01 to 
      2014:12. 
    
       `r fa("download", fill = "#ee5863")` 
       ```{r echo = FALSE} 
       xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
         name = "R code.xlsx")
       ```  
       &ensp;&ensp;
       `r fa("desktop", fill = "forestgreen")` 
       [View post](https://gcabrerag.rbind.io/)

    - Out-of-sample test results, from 1990:01 to 2014:12. 
    
       `r fa("download", fill = "#ee5863")` 
       ```{r echo = FALSE} 
       xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
         name = "R code.xlsx")
       ```  
       &ensp;&ensp;
       `r fa("desktop", fill = "forestgreen")` 
       [View post](https://gcabrerag.rbind.io/)

    - Asset allocation: CER gains and Sharpe Ratios. 
    
       `r fa("download", fill = "#ee5863")` 
       ```{r echo = FALSE} 
       xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
         name = "R code.xlsx")
       ```  
       &ensp;&ensp;
       `r fa("desktop", fill = "forestgreen")` 
       [View post](https://gcabrerag.rbind.io/)

5. Time-Series Momentum: Is It There? (Huang, Li, Wang and Zhou, 2018)

    `r fa("download", fill = "#ee5863")` 
    ```{r echo = FALSE} 
    xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
      name = "data.xlsx")
    ```   

    - Bootstrapped *t-statistic* of TSM with pooled regression and without 
      volatility scaling.
      
       `r fa("download", fill = "#ee5863")` 
       ```{r echo = FALSE} 
       xfun::embed_files(here::here("static", "datasets", "IMDb_tv_ratings"),
         name = "R code.xlsx")
       ``` 
       &ensp;&ensp;
       `r fa("desktop", fill = "forestgreen")` 
       [View post](https://gcabrerag.rbind.io/)
